This is a title

### 2021-05-27 manuscript/ms.tex
another (and hopefully final) major overhaul of the theory

\newcommand{\angles}[1]{\langle #1 \rangle}
\newcommand{\pd}[1]{\partial_{#1}}
\renewcommand{\vec}[1]{\boldsymbol{#1}}
\newcommand{\M}[1]{\mathbf{#1}}
\renewcommand{\dot}{\vec{\cdot}}
\newcommand{\grad}{\vec{\nabla}}
\newcommand{\cross}{\vec{\times}}
\newcommand{\laplacian}{\nabla^2}

@@

\section{Theory}
\label{sec:theory}
Throughout this work, we will utilize a modified version of the incompressible Boussinesq equations of motion,
\begin{align}
&\grad\dot\vec{u} = 0 
\label{eqn:incompressible} \\
&\partial_t \vec{u} + \vec{u}\dot\grad\vec{u} = -\frac{1}{\rho_0}\grad p + \frac{\rho_1}{\rho_0}\vec{g} + \nu\grad^2 \vec{u} 
\label{eqn:momentum} \\
&\partial_t T + \vec{u}\dot\grad T + w \gradad + \grad\dot[-k \grad \overline{T}] = \chi\grad^2 T' + Q
\label{eqn:temperature} \\
&\frac{\rho_1}{\rho_0} = -|\alpha| T.
\label{eqn:boussinesq}
\end{align}
Here, the density is decomposed into a (constant) background $\rho_0$ with fluctuations $\rho_1$ which appear only in the buoyancy force and depend on the temperature $T$ and the coefficient of thermal expansion $\alpha = \partial\ln\rho / \partial T$.
We furthermore define the velocity vector $\vec{u}$, the viscous diffusivity $\nu$, the thermal diffusivity $\chi$, the bulk internal heating $Q$ \citep[as in e.g.,][]{goluskin_vanderpoel_2016}, and the adiabatic temperature gradient $\gradad$.
We define $\gradad$ as a positive value to align with stellar structure conventions; thus marginal stability is achieved when $\partial_z T = -\gradad$.
These equations are similar to those derived by \citet{spiegel_veronis_1960} and utilized by e.g., \citet{korre_etal_2019}, but we allow the mean temperature profile $\overline{T}$ to carry a radiative flux $\Frad = -k \grad \overline{T}$, where $k$ is a radiative diffusivity which can vary with height.
The classic Boussinesq thermal diffusion term $\chi \grad^2 T'$ therefore carries no flux and acts only on the fluctuations away from the mean temperature profile, $T' \equiv T - \overline{T}$; throughout this work, we will represent horizontal averages with bars ($\overline{\,\cdot\,}$) and primes ($'$) represent fluctuations away from those horizontal means.
Throughout this work, we will consider Cartesian coordinates $(x, y, z)$, but this analysis is generalizeable to spherical geometry.
We will furthermore assume a model in which an unstable convection zone sits below a stable radiative zone, but this analysis also holds for the inverted problem.

\citet{zahn1991} theorized that the size of the convection zone is determined by the horizontally-averaged energy fluxes.
Assuming convection reaches a time-stationary state, we horizontally-average the vertically integrated Eqn.~\ref{eqn:temperature} to find
\begin{equation}
\overline{\Ftot} = \overline{\Frad} + \overline{\Fconv} = \int Q dz + \Fbot,
\end{equation}
where $\overline{\Fconv} = \overline{w T}$, is $\Fbot$ the flux carried at the bottom of the considered domain, and $\overline{\Ftot}$ is the total flux, which can vary in height due to the heating $Q$.
We next assume that convection penetrates above the Schwarzschild boundary of the convection zone at $z = L_s$ and mixes the temperature gradient to the adiabatic in the region $z \in [L_s, L_s + \delp]$, where $\delp$ is the penetration depth.
This assumption specifies the convective flux in the penetrative region,
\begin{equation}
\overline{\Fconv}(z \in [L_s, L_s + \delp]) = \Ftot - \overline{F_{\rm{rad, ad}}} = \Ftot - k \grad_{\rm{ad}}.
\label{eqn:fconv_pz}
\end{equation}
At this point it is useful to define the radiative gradient, $\grad_{\rm{rad}} = \Ftot/k$.
Within the penetrative region, $\grad_{\rm{ad}} > \grad_{\rm{rad}}$, so Eqn.~\ref{eqn:fconv_pz} requires $\overline{\Fconv} < 0$.
Following \citet{zahn1991}, we next assume that the velocity and horizontal temperature fluctuations are highly correlated and specified by a function $h(x,y)$,
\begin{equation}
w(x,y,z) = W(z)h(x,y),
\qquad
T'(x,y,z) = \delta T(z)h(x,y).
\end{equation}
The incompressibility constraint (Eqn.~\ref{eqn:incompressible}) specifies $\overline{w} = 0$, so $\overline{h} = 0$.
However, nonlinear interactions do not disappear when horizontally averaged, so $\overline{h^2} \neq 0$.
A vertically-varying formulation of the mean convective flux follows from this formulation,
\begin{equation}
\overline{\Fconv} \equiv \overline{w T} = \overline{h^2} \, W(z) \, \delta T(z).
\label{eqn:Fconv_vertical}
\end{equation}
In the penetrative region, since $\Fconv < 0$, $W(z)$ and $\delta T(z)$ must have opposite signs; the buoyancy force will therefore decelerate penetrative flows.
In a stationary state, the penetrative zone is thus described by a balance between advection and buoyancy in the vertical momentum equation (Eqn.~\ref{eqn:momentum} with Eqn.~\ref{eqn:boussinesq}), 
\begin{equation}
\frac{1}{2}\frac{d w^2}{dz} \sim |\alpha| g T'.
\end{equation}
Multiplying both sides by $h(x,y)$, horizontally averaging, and then eliminating $\delta T(z)$ using Eqn.~\ref{eqn:Fconv_vertical}, we retrieve a simple ordinary differential equation describing convective dynamics,
\begin{equation}
\frac{\overline{h^3}}{6 |\alpha| g \overline{h^2}} dW^3 \sim \overline{\Fconv} dz.
\label{eqn:theory_ode}
\end{equation}
While we have derived this expression in the penetrative zone, it should be equally valid in a stationary convection zone; there, however, $\overline{\Fconv} > 0$.
This equation can be integrated over the depth of the convection zone (from $W = 0$ at $z = 0$ to $W = W_0$ at $z = L_s$), as well as over the penetration zone (from $W = W_0$ at $z = L_s$ to $W = 0$ at $z = L_s + \delp$).
We assume however that the horizontal structure $h$ of the flux-carrying flows is not identical in the convection zone (CZ) and the penetration zone (PZ).
Taking the ratio of these two integrals of Eqn.~\ref{eqn:theory_ode}, we find
\begin{equation}
\mD \equiv \frac{(\overline{h^3}/\overline{h^2})_{\rm{PZ}}}{(\overline{h^3}/\overline{h^2})_{\rm{CZ}}},\qquad\qquad
\frac{\int_{\rm{PZ}} \overline{\Fconv} dz}{\int_{\rm{CZ}} \overline{\Fconv} dz} = - \mD.
\label{eqn:theory_fraction}
\end{equation}
This equation represents the central result of \citet{zahn1991}'s theory: the ratio of the vertically integrated convective fluxes in the PZ and CZ is directly linked to some constant which is determined by the structure of the dynamics ($\mD$).

Eqn.~\ref{eqn:theory_fraction} is however not intuitively satisfying.
In order to derive a specific prediction for the PZ depth, it is necessary to specify the vertical shape of $\overline{\Fconv}$.
We will study two cases in this work: a discontinuous jump in $\overline{\Fconv}$ at the convective boundary, and continuous piecewise-linear profile of $\overline{\Fconv}$ whose derivative may be discontinuous at the convective boundary.
In both of these cases, we will define a nondimensional ``Penetration Parameter,''
\begin{equation}
\mP \equiv -\frac{\overline{\Fconv}(z = L_s - \epsilon)}{\overline{\Fconv}(z = L_s + \epsilon)},
\label{eqn:theory_P_defn}
\end{equation}
which is the negative ratio of the convective flux some equidistant length $\epsilon$ both above and below the Schwarzschild convective boundary (assuming the region above the boundary is an adiabatic penetrative zone).

\subsection{Case I: Discontinuous flux}
\label{sec:discontinuous_theory}
We first consider a model which satisfies
\begin{equation}
\overline{\Fconv}(z) = \Fcz \begin{cases}
1			&	z \leq \Lcz,\\
-\mP_D^{-1}  & 	z > \Lcz 
\end{cases}.
\end{equation}
Here, $\Fcz$ is a (constant) value of flux carried in the convection zone and $\mP_D^{-1}$ is the penetration parameter (subscript D for discontinuous case).
Plugging this functional form of the flux into Eqn.~\ref{eqn:theory_fraction}, and integrating the convection zone from $z = 0$ to $z = L_p$ and the penetration zone from $z = L_p$ to $z = L_p + \delp$,
\begin{equation}
\frac{\delp}{L_s} = \mP_D \mD.
\label{eqn:discontinuous_prediction}
\end{equation}
We see that the size of the penetration region is linearly proportional to $\mP_D$ and is a function of the structure of the convective dynamics ($\mD$).
Intuitively, this result makes sense: as $\mP_D$ grows, the magnitude of $\overline{\Fconv}$ and the breaking force of buoyancy in the PZ shrink, resulting in larger penetrative regions.

\subsection{Case II: Piecewise linear flux}
\label{sec:linear_theory}
We next assume that $\overline{\Fconv}(z)$ is not discontinuous at the CZ-PZ boundary, but that its derivative may be,
\begin{equation}
\overline{\Fconv}(z) = 
\frac{\partial \Frad}{\partial z}\bigg|_{\rm{cz}}
\begin{cases}
(L_p - z) & z \leq L_p \\
-\mP_L^{-1} (z - L_p) & z > L_p
\end{cases},
\end{equation}
where $(\partial \Frad / \partial z)|_{\rm{cz}}$ is a constant and $\mP_L$ is the penetration parameter (subscript L for linear case).
Again, solving Eqn.~\ref{eqn:theory_fraction} with this functional form of the flux, we retrieve
\begin{equation}
\frac{\delp}{L_p} = \sqrt{\mP_L \mD},
\label{eqn:linear_prediction}
\end{equation}
which is identical to the prediction of \citet{zahn1991} when we take $\mP_L = 1$.
In this work, we will test the predictions of Eqns.~\ref{eqn:discontinuous_prediction} and \ref{eqn:linear_prediction}.
Our aim is to see if the predicted scalings with the penetration parameter $\mP$ are realized in direct numerical simulations, and to measure preliminary values for $\mD$ in local simulations.

@@

\section{Accelerated Evolution}
\label{app:accelerated_evolution}
As demonstrated in Fig.~\ref{fig:time_evolution}, the time evolution of simulations which start from a state based on the Schwarzschild criterion can be prohibitively long.
In \citet{anders_etal_2018}, we explored the long time evolution of simple convective simulations and found that fast-forwarding the evolution of a convective simulation's internal energy and thermal structure is possible.
In this work, we accelerate the evolution of of our simulations in order to more quickly determine the final size of the evolved penetration zones according to the following algorithm.
\begin{enumerate}
\item Once a simulation has a volume-averaged Reynolds number greater than 1, we wait 50 freefall times.
\item We measure the 50\% departure point ($\delta_p$) of the top of the convection zone every freefall time, and store this information for 50 freefall times.
\item We measure $d\delta_p/dt$ using NumPy's \texttt{gradient} function. 
If the average value of $d\delta_p/dt$ has a different sign over the first and last 25 freefall times in our collection window, we erase the first 25 freefall times of data and return to step 2 for 25 freefall times.
If the average value of $d\delta_p/dt$ has the same sign over the first and last 25 freefall times, we accelerate the evolution of our simulations.
\item We calculate $\Delta\delta_p$ as the minimum of 
\begin{equation}
\Delta\delta_{p,1} = \overline{\frac{d\delta_p}{dt}}\bigg|\frac{\Delta \delta_p}{\Delta d \delta_p / dt} \bigg|,\qquad
\Delta\delta_{p,2} = 500\overline{\frac{d\delta_p}{dt}}.
\end{equation}
Here, $\Delta\delta_{p,1}$ essentially represents a newton iteration in $d\delta_p / dt$ vs. $\delta_p$ space towards the root value where $d\delta_p / dt = 0$.
In some cases, $\Delta\delta_{p,1}$ becomes too large; we thus limit the maximum change to $\Delta\delta_{p,2}$, which represents an advancement of the convective boundary at the current evolutionary pace by 500 freefall time units.
\item After determining a new value of $\delta_{\rm{p,ev}} = \delta_{p,0} + \Delta\delta_p$, we adjust the $m = 0$ temperature gradient to
\begin{equation}
\partial_z \overline{T} = -\gradad - H(z; \delta_{\rm{p,ev}}, 0.05) \Delta\grad,
\label{eqn:initial_grad}
\end{equation}
where $H$ is defined in Eqn.~\ref{eqn:heaviside} and $\Delta\grad = \gradrad - \gradad$.
We also multiply the temperature perturbations and full convective velocity field by $H(z; 1, 0.05)$.
This sets all fluctuations above the nominal Schwarzschild convection zone to zero, thereby avoiding any strange dynamical transients caused by the the old dynamics at the radiative-convective boundary (which has moved as a result of this process).
\item We restart from step 1.
\end{enumerate}
If a simulation returns to step 2 from step 3 ten times over the course of its evolution, we assume that it has converged near its answer, stop this iterative loop, and allow the simulation to timestep normally.
This process effectively removes the long diffusive thermal evolution on display in the middle panel of Fig.~\ref{fig:time_evolution} by immediately setting the mean temperature profile to the radiative profile above the PZ.

>>>>

\newcommand{\angles}[1]{\langle #1 \rangle}
\newcommand{\pd}[1]{\partial_{#1}}
\renewcommand{\vec}[1]{\boldsymbol{#1}}
\newcommand{\M}[1]{\mathbf{#1}}
\renewcommand{\dot}{\vec{\cdot}}
\renewcommand{\bar}[1]{\overline{#1}}
\newcommand{\grad}{\vec{\nabla}}
\newcommand{\cross}{\vec{\times}}
\newcommand{\laplacian}{\nabla^2}

@@

\section{Theory}
\label{sec:theory}

\subsection{Equations}
\label{sec:theory_equations}
Throughout this work, we will utilize a modified version of the incompressible Boussinesq equations of motion,
\begin{align}
&\grad\dot\vec{u} = 0 
\label{eqn:incompressible} \\
&\partial_t \vec{u} + \vec{u}\dot\grad\vec{u} = -\frac{1}{\rho_0}\grad p + \frac{\rho_1}{\rho_0}\vec{g} + \nu\grad^2 \vec{u} 
\label{eqn:momentum} \\
&\partial_t T + \vec{u}\dot\grad T + w \gradad + \grad\dot[-k \grad \overline{T}] = \chi\grad^2 T' + Q
\label{eqn:temperature} \\
&\frac{\rho_1}{\rho_0} = -|\alpha| T.
\label{eqn:boussinesq}
\end{align}
Here, the density is decomposed into a (constant) background $\rho_0$ with fluctuations $\rho_1$ which appear only in the buoyancy force and depend on the temperature $T$ and the coefficient of thermal expansion $\alpha = \partial\ln\rho / \partial T$.
We furthermore define the velocity vector $\vec{u}$, the viscous diffusivity $\nu$, the thermal diffusivity $\chi$, the bulk internal heating $Q$ \citep[as in e.g.,][]{goluskin_vanderpoel_2016}, and the adiabatic temperature gradient $\gradad$.
We define $\gradad$ as a positive value to align with stellar structure conventions; thus marginal stability is achieved when $\partial_z T = -\gradad$.
These equations are similar to those derived by \citet{spiegel_veronis_1960} and utilized by e.g., \citet{korre_etal_2019}, but we allow the mean temperature profile $\overline{T}$ to carry a radiative flux $\Frad = -k \grad \overline{T}$, where $k$ is a radiative diffusivity which can vary with height.
The classic Boussinesq thermal diffusion term $\chi \grad^2 T'$ therefore carries no flux and acts only on the fluctuations away from the mean temperature profile, $T' \equiv T - \overline{T}$; throughout this work, we will represent horizontal averages with bars ($\overline{\,\cdot\,}$) and primes ($'$) represent fluctuations away from those horizontal means.
Throughout this work, we will consider Cartesian coordinates $(x, y, z)$, but this analysis is generalizeable to spherical geometry.
We will furthermore assume a model in which an unstable convection zone sits below a stable radiative zone, but this analysis also holds for the inverted problem.

%\subsection{Vertical momentum equation balances}
%\label{sec:theory_momentum}
%Assuming a vertical and uniform gravitational acceleration $\vec{g} = -g\hat{z}$, the vertical component of Eqn.~\ref{eqn:momentum} with Eqn.~\ref{eqn:boussinesq} is
%\begin{equation}
%\partial_t w + (\vec{u}\dot\grad)w = -\frac{1}{\rho_0}\partial_z p + |\alpha|g T + \nu\grad^2 w.
%\label{eqn:momentum_z}
%\end{equation}
%We next horizontally average this equation; under the assumption that $\overline{w} = 0$ at some height (e.g., at an impenetrable boundary), Eqn.~\ref{eqn:incompressible} requires $\overline{w}$ = 0 everywhere.
%The horizontally-averaged equation is therefore
%\begin{equation}
%\frac{1}{\rho_0}\frac{d \overline{p}}{dz} = |\alpha| g \overline{T} - \overline{(\vec{u}\dot\grad)w} + \nu\overline{\grad_h^2 w},
%\end{equation}
%where $\grad_h^2 = \partial_x^2 + \partial_y^2$.
%At this point we decompose $\overline{p} = \overline{p_s} + \overline{p_d}$, where $p_s$ is the ``structure'' component of of the pressure whose gradient balances the buoyant gradient (providing hydrostatic balance), and $p_d$ is the dynamical pressure whose mean balances the mean contributions of advection and dissipation.
%Accordingly, we define $\tilde{p} \equiv p - \overline{p_s}$, removing the mean structure component of the pressure.
%This construction leaves fluctuations ($p'$ and $\overline{p_d}$) which are set by the convective dynamics.
%Taking a time-average of Eqn.~\ref{eqn:momentum_z} and assuming that convection reaches a statistically stationary state and that viscous dissipation is unimportant \citep[which is a common assumption, but may not always apply in stellar contexts per][]{currie_browning_2017}, we retrieve
%\begin{equation}
%\frac{1}{\rho_0}\frac{\partial \tilde{p}}{\partial z} = |\alpha| g T' - (\vec{u}\dot\grad)w.
%\label{eqn:fluc_momentum_z}
%\end{equation}
%In other words, convection reaches a state in which fluctuating buoyancy forces and nonlinear advection come into a balance and saturate at similar magnitudes.
%The pressure gradient rises to a similar magnitude to regulate the flows and ensure Eqn.~\ref{eqn:incompressible} is satisfied (and a similar argument could be made for e.g., anelastic convection).
%As a result, we can estimate that each of the terms in this equation have similar magnitudes,
%\begin{equation}
%\frac{1}{\rho_0}\frac{\partial \tilde{p}}{\partial z} \sim |\alpha| g T' \sim (\vec{u}\dot\grad)w.
%\label{eqn:momentum_balance}
%\end{equation}

\subsection{Kinetic energy \& the vorticity-flux link}
\label{sec:theory_energy}
Taking an inner product of the velocity and Eqn.~\ref{eqn:momentum} reveals the kinetic energy equation,
\begin{equation}
\frac{\partial}{\partial t}\left(\frac{|\vec{u}|^2}{2}\right) 
+ \grad\dot\left[\vec{u}\left(\frac{|\vec{u}|^2}{2} + \frac{p}{\rho_0}\right) - \nu\vec{u}\cross\vec{\omega}\right]
= \alpha g w T - \nu|\vec{\omega}|^2,
\label{eqn:kinetic_energy}
\end{equation}
where $\vec{\omega} = \grad\cross\vec{u}$ is the vorticity and $|\vec{u}|^2 = \vec{u}\dot\vec{u}$ \& $|\vec{\omega}|^2 = \vec{\omega}\dot\vec{\omega}$.
Assuming a statistically stationary state, and assuming that the kinetic energy fluxes vanishes at the upper and lower boundaries of the convection zone, this equation permits one solution,
\begin{equation}
\alpha g \angles{\Fconv} = \nu\angles{|\vec{\omega}|^2},
\label{eqn:ke_averages}
\end{equation}
where $\Fconv = w T$ and angles $\angles{\,\cdot\,}$ represent a time- and volume- average.
It is counterintuitive to find that a viscous term is on the same order of magnitude as the convective flux.
However, this term dimensionally behaves like $\nu u^2 / \ell^2$, where $\ell$ is the length scale of velocity gradients; if the average vorticity is dominated by gradients at the dissipation scale, then it makes sense that this term can persist even at small values of $\nu$.
Furthermore, \citet{currie_browning_2017} demonstrated that even in appreciably density-stratified atmospheres, the magnitude of the viscous heating term remains large for turbulent flows.
Since $\nu |\vec{\omega}^2|$ is the Boussinesq analog to the viscous heating, the importance of this term is perhaps not too surprising.

We now decompose the convection zone into a zone which is classically unstable according to the Schwarzschild criterion (called the CZ, with depth $L_s$) and a dynamically distinct penetrative zone (called the PZ, with depth $\delp$).
Following Eqn.~\ref{eqn:ke_averages}, we can write
\begin{equation}
\int_{\rm{CZ}} \bar{\Fconv} dz + \int_{\rm{PZ}} \bar{\Fconv} dz = \frac{\nu}{\alpha g}(L_s + \delp) \angles{|\vec{\omega}|^2}.
\label{eqn:flux_breakup}
\end{equation}
Rearranging, we can write
\begin{equation}
\frac{\int_{\rm{PZ}}\bar{\Fconv}\,dz}{\int_{\rm{CZ}}\bar{\Fconv}\,dz} = -(1 - f),
\qquad\rm{with}\qquad
f \equiv \frac{\nu}{\alpha g}(L_s + \delp) \frac{\angles{|\vec{\omega}|^2}}{\int_{\rm{CZ}} \bar{\Fconv} dz}
= \frac{\int_{\rm{CZ+PZ}}\bar{\Fconv}\,dz}{\int_{\rm{CZ}}\bar{\Fconv}\,dz},
\label{eqn:preliminary_flux_ratio}
\end{equation}
where the final equality is a tautological rearrangement of the decomposition of the flux integral in Eqn.~\ref{eqn:flux_breakup}.
The upshot of this equation is that the ratio of the flux integrals in the PZ and CZ relates to some characteristic properties of the convective dynamics.
In order to say more, we must turn to a more in-depth examination of the fluxes in the PZ.

%
%Again neglecting viscosity, averaging horizontally and in time, and assuming a statistically stationary state, we retrieve
%\begin{equation}
%\frac{d}{dz}\left[\frac{\overline{w u^2}}{2} + \frac{\overline{w\tilde{p}}}{\rho_0}\right]
%= \alpha g \overline{\Fconv},
%\label{eqn:mean_ke}
%\end{equation}
%At this point we now assume that the velocities are vertically dominated or isotropic so that $u^2 \sim w^2$.
%We furthermore assume that the balance in Eqn.~\ref{eqn:momentum_balance} is roughly correct, so that $\overline{w\tilde{p}} \sim \rho_0 \overline{w^3}$.
%Under these assumptions, we retrieve
%\begin{equation}
%\frac{d \overline{w^3}}{dz} \sim \alpha g \overline{\Fconv}
%\Rightarrow
%\frac{d \overline{w^3}}{dz} \approx \varsigma \alpha g \overline{\Fconv},
%\label{eqn:velocity_ode}
%\end{equation}
%where $\varsigma$ is a fudge factor which describes the quality of the assumptions we have made, and the fact that e.g., $w^2 < u^2$, the balance of Eqn.~\ref{eqn:momentum_balance} likely only holds to a factor of a few, etc..
%This equation is logically analagous to one used between Eqn.~3.8 \& 3.9 of \citet{zahn1991}, but we have not relied upon the assumption of a vertically invariant convective planform which likely does not hold for turbulent dynamics.
%Eqn.~\ref{eqn:velocity_ode} is also intuitively satisfying; it says that roughly $\overline{w^3} \sim \overline{\Fconv}$, which fits intuition from mixing length theory.
%
\subsection{A flux-based penetration argument}
\citet{zahn1991} theorized that the size of the convection zone is determined by the horizontally-averaged energy fluxes.
Assuming convection reaches a time-stationary state, we horizontally-average and vertically integrate Eqn.~\ref{eqn:temperature} to find
\begin{equation}
\overline{\Ftot} = \overline{\Frad} + \overline{\Fconv} = \int Q dz + \Fbot,
\end{equation}
where $\Fbot$ is the flux carried at the bottom of the considered domain, and $\overline{\Ftot}$ is the total flux, which can vary in height due to the heating $Q$.
We next assume that convection penetrates above the Schwarzschild boundary of the convection zone at $z = L_s$ and mixes the temperature gradient to the adiabatic in the region $z \in [L_s, L_s + \delp]$, where $\delp$ is the penetration depth.
This assumption specifies the convective flux in the penetrative region,
\begin{equation}
\overline{\Fconv}(z \in [L_s, L_s + \delp]) = \Ftot - \overline{F_{\rm{rad, ad}}} = \Ftot - k \grad_{\rm{ad}}.
\label{eqn:fconv_pz}
\end{equation}
At this point it is useful to define the radiative gradient, $\grad_{\rm{rad}} = \Ftot/k$.
Within the penetrative region, $\grad_{\rm{ad}} > \grad_{\rm{rad}}$, so Eqn.~\ref{eqn:fconv_pz} requires $\overline{\Fconv} < 0$.

With the knowledge that $\Fconv$ is negative in the PZ, we rewrite Eqn.~\ref{eqn:preliminary_flux_ratio}
\begin{equation}
\frac{|\int_{\rm{PZ}}\bar{\Fconv}\,dz|}{\int_{\rm{CZ}}\bar{\Fconv}\,dz} = (1 - f),
\label{eqn:theory_fraction}
\end{equation}
and note that $f < 1$ by its flux-based definition.
While we have arrived here in a very different manner, this equation represents the central result of \citet{zahn1991}'s theory: the ratio of the vertically integrated convective fluxes in the PZ and CZ is directly linked to some constant which relates to the convective dynamics.
More importantly, if $\bar{\Fconv}$, and $f$ are known, this ratio directly sets the size of the PZ.

In order to derive a specific prediction for the PZ depth, it is necessary to specify the vertical shape of $\overline{\Fconv}$.
We will study two cases in this work, laid out below.
In both of these cases, we will define a nondimensional ``Penetration Parameter,''
\begin{equation}
\mP \equiv -\frac{\overline{\Fconv}(z = L_s - \epsilon)}{\overline{\Fconv}(z = L_s + \epsilon)},
\label{eqn:theory_P_defn}
\end{equation}
which is the negative ratio of the convective flux some equidistant length $\epsilon$ both above and below the Schwarzschild convective boundary $L_s$ (assuming the region above the boundary is an adiabatic penetrative zone).

\subsubsection{Case I: Discontinuous flux}
\label{sec:discontinuous_theory}
We first consider a model which satisfies
\begin{equation}
\overline{\Fconv}(z) = \Fcz \begin{cases}
1			&	z \leq \Lcz,\\
-\mP_D^{-1}  & 	z > \Lcz 
\end{cases}.
\end{equation}
Here, $\Fcz$ is a (constant) value of flux carried in the convection zone and $\mP_D$ is the penetration parameter (subscript D for discontinuous case).
Plugging this functional form of the flux into Eqn.~\ref{eqn:theory_fraction}, and integrating the convection zone from $z = 0$ to $z = L_s$ and the penetration zone from $z = L_s$ to $z = L_s + \delp$, we predict
\begin{equation}
\frac{\delp}{L_s} = \mP_D (1 - f).
\label{eqn:discontinuous_prediction}
\end{equation}
Assuming that $f$ is a weak function of $\mP_D$, we see that the size of the penetration region is linearly proportional to $\mP_D$.
Intuitively, this result makes sense: as $\mP_D$ grows, the magnitude of $\overline{\Fconv}$ and the breaking force of buoyancy in the PZ shrink, resulting in larger penetrative regions.
Furthermore, if $\mP_D$ doubles, the PZ magnitude of $\Fconv$ halves, and if $f$ does not change then the PZ must also double in size according to Eqn.~\ref{eqn:ke_averages}.

\subsubsection{Case II: Piecewise linear flux}
\label{sec:linear_theory}
We next assume that $\overline{\Fconv}(z)$ is not discontinuous at the CZ-PZ boundary, but that its derivative may be,
\begin{equation}
\overline{\Fconv}(z) = 
\frac{\partial \Frad}{\partial z}\bigg|_{\rm{cz}}
\begin{cases}
(L_p - z) & z \leq L_p \\
-\mP_L^{-1} (z - L_p) & z > L_p
\end{cases},
\end{equation}
where $(\partial \Frad / \partial z)|_{\rm{cz}}$ is a constant and $\mP_L$ is the penetration parameter (subscript L for linear case).
Again, solving Eqn.~\ref{eqn:theory_fraction} with this functional form of the flux, we retrieve
\begin{equation}
\frac{\delp}{L_p} = \sqrt{\mP_L (1 - f)}.
\label{eqn:linear_prediction}
\end{equation}

In this work, we will test the predictions of Eqns.~\ref{eqn:discontinuous_prediction} and \ref{eqn:linear_prediction}.
Our goals are to see if the predicted scalings with the penetration parameter $\mP$ are realized in simulations, and to measure preliminary values for $\mD$ in local simulations.

@@

\section{Accelerated Evolution}
\label{app:accelerated_evolution}
As demonstrated in Fig.~\ref{fig:time_evolution}, the time evolution of simulations which start from a state based on the Schwarzschild criterion can be prohibitively long.
In \citet{anders_etal_2018}, we explored the long time evolution of simple convective simulations and found that fast-forwarding the evolution of a convective simulation's internal energy and thermal structure can be done accurately.
In this work, we accelerate the evolution of of our simulations in order to more quickly determine the final size of the evolved penetration zones according to the following algorithm.
\begin{enumerate}
\item Once a simulation has a volume-averaged Reynolds number greater than 1, we wait 10 freefall times to allow dynamical transients to pass.
\item We measure the departure points ($\delta_{0.1}$, $\delta_{0.5}$, $\delta_{0.9}$) every freefall time, and store this information for 30 freefall times.
\item We linearly fit each of the departure points' evolution against time using NumPy's \texttt{polyfit} function.
We assume that convective motions influence $\delta_{0.1}$ and $\delta_{0.5}$ more strongly than $\delta_{0.9}$.
We measure the time-evolution of the convective front $\frac{d \delp}{dt}$ by averaging the slope of the linear fits for $\delta_{0.1}$ and $\delta{0.2}$.
\item We take a large ``time step'' of size $\tau_{\rm{AE}}$ forward.
We calculate $\Delta \delta_p = \tau_{\rm{AE}} \frac{d \delp}{dt}$.
\begin{itemize}
\item If $\Delta \delta_p < 0.005$, we erase the first 15 time units worth of departure point measures and return to step 2 for 15 time units.
\item  If $\Delta \delta_p$ is large, we adjust the top of the PZ by setting $\delta_{0.5,\rm{new}} = \angles{\delta_{0.5}}_t + \Delta \delta_p$.
If $\Delta \delta_p > 0.05$, we limit its value to 0.05.
We calculate the width of the thermal adjustment layer $\delta_w$ as the minimum of $\angles{\delta_{0.9} - \delta_{0.5}}_t$ and $\angles{\delta_{0.5} - \delta_{0.1}}_t$.
We adjust the $m = 0$ temperature gradient to
\begin{equation}
\partial_z \overline{T} = -\gradad - H(z; \delta_{\rm{0.5,\rm{new}}}, \delta_w) \Delta\grad,
\label{eqn:initial_grad}
\end{equation}
where $H$ is defined in Eqn.~\ref{eqn:heaviside} and $\Delta\grad = \gradrad - \gradad$.
We also multiply the temperature perturbations and full convective velocity field by $H(z; 1, 0.05)$.
This sets all fluctuations above the nominal Schwarzschild convection zone to zero, thereby avoiding any strange dynamical transients caused by the the old dynamics at the radiative-convective boundary (which has moved as a result of this process).
\end{itemize}
\item We restart from step 1.
\end{enumerate}
If a simulation returns to step 2 from step 4 ten times over the course of its evolution, we assume that it has converged near its answer, stop this iterative loop, and allow the simulation to timestep normally.
This process effectively removes the long diffusive thermal evolution on display in the middle panel of Fig.~\ref{fig:time_evolution} by immediately setting the mean temperature profile to the radiative profile above the PZ.
